### 2018-02-09 Writing/Thesis/content/chapter-evaluation.tex
More writing & some meta data calcs

@@

% Generating base performance data

% Oracle

% Best Algo Performance
Both variants compared against Best Algorithm baseline, which was implemented as a Ranker of type PreferenceRanker itself and evaluated the same way as the other PreferenceRankers. This baseline is computed iteratively by training an oracle on the same data set and then

% Evaluation Measures used & computed

@@

% Insights about classifiers: place best ranking, min, max rank (optional) for each classif?
% TODO replace by large data set
\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X}
		%\hline
		Classifier		&	Number of Data Sets Placed First \\	\hline
		Logistic			&	28								\\	\hline	
		Naive Bayes			&	29								\\	\hline	
		IBk		&	23								\\	\hline	
		KStar			&	24								\\	\hline	
		LMT		&	17								\\	\hline	
		VotedPerceptron		&	16								\\	\hline	
		ZeroR		&	14								\\	\hline	
		J48			&	13								\\	\hline	
		NaiveBayesMultinomial			&	6								\\	\hline	
		RandomTree			&	2								\\	\hline	
		SimpleLogistic			&	1								\\	\hline
		DecisionStump			&	1								\\	\hline
		MultilayerPerceptron			&	1								\\	\hline
		RandomForest			&	1								\\	\hline
		DecisionTable			&	1								\\	\hline
		PART			&	1								\\	\hline
		SGD			&	1								\\	\hline
		BayesNet			&	1								\\	\hline
		REPTree			&	1								\\	\hline
		JRip			&	1								\\	\hline
		SMO			&	313								\\	\hline
		OneR			&	448								\\	\hline

	\end{tabularx}
	\label{tab:table1}
	\caption{The ranking }
\end{table}

\pgfplotsset{width=\textwidth}
\begin{tikzpicture}
\begin{axis}
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=Loss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=Loss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
\legend{IB Label KY, Best Algorithm}
\end{axis}
\end{tikzpicture}

>>>>

\section{Baseline and Oracle}
% Workings of oracle
In order to evaluate the implemented rankers, their outputs are compared to a perfect output generated by an oracle. The oracle is implemented as a ranker that, after having been trained on a meta data - performance data set returns correct rankings when queried for any instance of that data set. The correct ranking is implied by the performance values (highest first, as the measure used here is predictive accuracy), with ties being handled in a sequential manner, i.e. for the same performance values, the algorithm that was encountered first when constructing the ranking will be ranked before all others with the same value.

% Evaluation Measures used & computed
As a ranking returned by this oracle represents the ideal solution,

% Baseline
Furthermore, we are interested in the question as to what degree knowing about the properties of a data set influences the quality of rankings. Therefore, a ranker that is agnostic of the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline. The baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the RMSE of predict performance values cannot bet computed. Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the baseline, and come as close as possible to the correct ranking.

@@

% Generating base performance data
Performance Values acquired with 5 times MCCV

@@

% Insights about classifiers: place best ranking, min, max rank (optional) for each classif?

\subsection{Accuracy}

\begin{landscape}
\begin{table}[h]
\centering
	\begin{tabularx}{23,7cm}{>{\hsize=3.4\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-13}
							 			& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 		& Min	& Max		& Mean		& Stdv	\\ \hline
		LinearRegression 				& -0.255 	& 0.896 		& 0.473	 	& 0.221 & 0 		& 86.667 	& 3.469	 	& 7.244 		& 0 		& 31.220 	& 1.267	 	& 3.011 	\\
		M5P				 				& -0.29 		& 0.870 		& 0.470	 	& 0.219 & 0 		& 82.353 	& 3.78	 	& 6.535 		& 0 		& 82.353 	& 1.508	 	& 4.757 	\\	
		RandomForest		 				& -0.281 	& 0.922 		& 0.495	 	& 0.228 & 0		& 60 		& 3.097 		& 5.745 		& 0 		& 34.634 	& 1.308	 	& 3.150 	\\	
		REPTree			 				& -0.229 	& 0.896 		& 0.412		& 0.213 & 0 		& 82.353		& 4.829	 	& 7.948 		& 0		& 34.634 	& 1.759	 	& 3.515 	\\	
		InstanceBased 					& -0.429 	& 0.870 		& 0.221	 	& 0.249 & 0 		& 82.353		& 5.401 		& 9.44 		& 0 		& 82.353 	& 3.62	 	& 8.540 	\\	
		InstanceBased\footnotemark{}		& -0.429 	& 0.887 		& 0.340	 	& 0.252 & 0 		& 98.367 	& 5.437 		& 10.323 	& 0 		& 82.353 	& 3.294	 	& 8.367 	\\	
		InstanceBased\footnotemark{}		& -0.429 	& 0.870 		& 0.335	 	& 0.249 & 0 		& 82.353 	& 5.382	 	& 9.402 		& 0 		& 82.353 	& 3.511	 	& 8.493 	\\	
		PairwiseComparison 				& -0.870 	& 0.576		& 0.014	 	& 0.234 & 0 		& 97.822 	& 9.762	 	& 13.135 	& 0 		& 82.353 	& 4.001	 	& 8.600 	\\	
		BestAlgorithm	 				& -0.437 	& 0.489 		& 0.057	 	& 0.159 & 0		& 82.353		& 6.480 		& 10.168 	& 0		& 82.353		& 3.420 		& 8.195 	\\							
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Evaluation results with full meta data}
\end{table}

\addtocounter{footnote}{-2}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}
\end{landscape}

\tikzsetnextfilename{LossGraphics}
\pgfplotsset{width=\textwidth}
\begin{tikzpicture}
\begin{axis}
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=Loss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=Loss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
\legend{IB Label KY, Best Algorithm}
\end{axis}
\end{tikzpicture}

\tikzsetnextfilename{BestThreeLossGraphics}
\pgfplotsset{width=\textwidth}
\begin{tikzpicture}
\begin{axis}
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
%\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
%\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
\legend{IB Label KY, Best Algorithm}
\end{axis}
\end{tikzpicture}

\subsection{Time}
\hspace{-1em}
\begin{table}[h]
	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Prediction Time (ms)} \\ \cline{2-9}
										& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 	\\ \hline
		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	& 0 		& 86.667 	& 3.469	 	& 7.244 	\\
		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	& 0 		& 82.353 	& 3.78	 	& 6.535	\\	
		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	& 0		& 60 		& 3.097 		& 5.745	\\	
		REPTree			 				& 599 		& 1264 		& 629		& 38 	& 0 		& 82.353		& 4.829	 	& 7.948	\\	
		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	& 0 		& 82.353		& 5.401 		& 9.44	\\	
		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	& 0 		& 98.367 	& 5.437 		& 10.323	\\	
		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	& 0 		& 82.353 	& 5.382	 	& 9.402	\\	
		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	& 0 		& 97.822 	& 9.762	 	& 13.135	\\	
		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23	 	& 0		& 82.353		& 6.480 		& 10.168	\\							
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Build and Prediction Times of the Rankers in ms}
\end{table}

\addtocounter{footnote}{-2}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}

\subsection{Further Insights}

\begin{table}[h]
	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} \\ \cline{2-5}
										& Min		& Max		& Mean		& Stdv 	\\ \hline
		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	\\
		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	\\	
		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	\\	
		REPTree			 				& 599 		& 1264 		& 629		& 38 	\\	
		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	\\	
		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	\\	
		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	\\	
		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	\\	
		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23		\\							
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Build and Prediction Times of the Rankers in ms}
\end{table}

% TODO replace by large data set??
\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X}
		%\hline
		Classifier				&	Number of Data Sets Placed First \\	\hline
		Logistic					&	28								\\	\hline	
		Naive Bayes				&	29								\\	\hline	
		IBk						&	23								\\	\hline	
		KStar					&	24								\\	\hline	
		LMT						&	17								\\	\hline	
		VotedPerceptron			&	16								\\	\hline	
		ZeroR					&	14								\\	\hline	
		J48						&	13								\\	\hline	
		NaiveBayesMultinomial	&	6								\\	\hline	
		RandomTree				&	2								\\	\hline	
		SimpleLogistic			&	1								\\	\hline
		DecisionStump			&	1								\\	\hline
		MultilayerPerceptron		&	1								\\	\hline
		RandomForest				&	1								\\	\hline
		DecisionTable			&	1								\\	\hline
		PART						&	1								\\	\hline
		SGD						&	1								\\	\hline
		BayesNet					&	1								\\	\hline
		REPTree					&	1								\\	\hline
		JRip						&	1								\\	\hline
		SMO						&	313								\\	\hline
		OneR						&	448								\\	\hline																	
	\end{tabularx}
	\label{tab:table1}
	\caption{The ranking of Classifiers returned by the Best Algorithm Baseline}
\end{table}
